Investigating the alternative prey hypothesis with the POMP framework

### 2024-04-23 draft.Rmd
small changes

```{r}
freeze(
  runif_design(
    lower = c(alpha = 0, Beta = 0, gamma = 0, a = 0, b = 0, c = 0,
              sigma_obs = 0, logF_0 = ivp(0.1), logB_0 = ivp(0.1),
              sigmaF = 0, sigmaB = 0.02, logRho = 0)
    upper = c(alpha = 0, Beta = 0, gamma = 0, a = 0, b = 0, c = 0,
              sigma_obs = 0, logF_0 = ivp(0.1), logB_0 = ivp(0.1),
              sigmaF = 0, sigmaB = 0.02, logRho = 0)
  ),
  seed = 420
) -> guesses
```

>>>>

```{r}

```

```{r}
freeze(
  runif_design(
    lower = c(alpha = 0, Beta = 0, gamma = 0, a = 0, b = 0, c = 0,
              sigma_obs = 0, logF_0 = ivp(0.1), logB_0 = ivp(0.1),
              sigmaF = 0, sigmaB = 0.02, logRho = 0),
    upper = c(alpha = 0, Beta = 0, gamma = 0, a = 0, b = 0, c = 0,
              sigma_obs = 0, logF_0 = ivp(0.1), logB_0 = ivp(0.1),
              sigmaF = 0, sigmaB = 0.02, logRho = 0)
  ),
  seed = 420
) -> guesses
```
